---
title: "linear mixed model with vector-valued random effects"
---

```{r echo=FALSE, eval=TRUE, results='hide',include=FALSE}
library(TMB)
source("../utils.R")
source("vectorMixed.R")
```


```{r}
library(lme4)
library(glmmTMB)

## fit basic model 
m1 <- lmer(Reaction ~ Days + (Days|Subject), sleepstudy, REML = FALSE)
glmmtmb1 <- glmmTMB(Reaction ~ Days + (Days|Subject), sleepstudy, REML = FALSE)
```

## checking glmmTMB vs lmer
## compare FE vcov
all.equal(as.matrix(vcov(m1)), vcov(glmmtmb1)$cond, tolerance = 1e-4)
## compare RE cov matrix
all.equal(c(VarCorr(m1)$Subject), c(VarCorr(glmmtmb1)$cond$Subject), tol = 1e-4)

all.equal(unname(glmmtmb1$fit$par),
          ## reorder parameters, and double logsd
          ##  (glmmTMB fits on the log-variance rather than the log-sd scale)
          unname(c(tmbfit1$par[1:2],
                   tmbfit1$par["logsd"]*2,
                   tmbfit1$par[3:5])),
          tolerance = 1e-6
          )

## try with BFGS
## ?? clearly suboptimal fit (5 log-likelihood units worse than tmbfit1 ...)
## would better starting values help??
## don't know what's going on here.
tmbfit2 <- with(obj, optim(par = par, fn = fn, gr = gr, method = "BFGS",
                           control = list(maxit = 200)))

